Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-06-01 manuscript.Rmd
Edits to crqa results

# Discussion
In the present study, we investigated the dynamics of real-world events
and online communication on Twitter in Syria during Arab Spring. We examined
how social mobilization both virtually and physically evolve over time in
tandem. Using the
nonlinear dynamical time series analyses, we investigated the theory that
virtual mobilization is increasingly reflective of real-world events
during times of strife.

## Cross-Recurrence Quantification Analysis
### Syria as Target
The significant result of DET for social cohesion with all and negative 
events supports our hypothesis that
event salience is coupled with online social cohesion The frequency
of all and negative events are thus associated with greater
shared trajectories with social cohesion that would be expected by chance. 
However, when we specifically target positive events, the connection
to social cohesion fades, providing further
support for our hypothesis. Positive events
may be less coupled to social cohesion than more salient negative events
during times of turmoil; by contrast, overall event frequency and
negative event frequency are coupled with Twitter social cohesion.

@@

While interesting, the underlying meaning or drivers of this change
in results requires further investigation that incorporates the
actual content of the tweets themselves. One possible reason (among
many) may be that the finding was spurious. The positive external 
events from Syria may have been self-serving, aiming to prevent intervention
by other countries or to cover up what was happening internally.
During these moments, the increased cohesion may reflect a surge from 
the Syrian people trying to raise awareness of the situation or
to decry the Syrian government's attempts to improve their international
standing. In this case, the increased coupling of positive events would
coupled not with shared positive affect in social media but instead
to shared negative affect in social media in response. However, we
cannot test this hypothesis with the current data; future  
research should explore the semantic content of this tweet
corpus to determine the nature of the socially cohered language.

>>>>

# Discussion
In the present study, we investigated the dynamics of real-world events
and online communication on Twitter in Syria during Arab Spring. We examined
how social mobilization both virtually and physically evolve over time in
tandem. Using nonlinear dynamical time series analyses, we investigated the 
theory that virtual mobilization is increasingly reflective of real-world 
events during times of strife.

## Cross-Recurrence Quantification Analysis
### Syria as Target
The significant result of DET for social cohesion with all and negative 
events supports our hypothesis that event salience is coupled with online 
social cohesion. The frequency of all and negative events are thus associated 
with greater shared trajectories with social cohesion that would be expected 
by chance. However, when we specifically target positive events, the connection
to social cohesion fades, providing further support for our hypothesis. 
Positive events may be less coupled to social cohesion than more salient 
negative events during times of turmoil; by contrast, overall event frequency 
and negative event frequency are coupled with Twitter social cohesion.

@@

While interesting, the underlying meaning or drivers of this change
in results requires further investigation that incorporates the
actual content of the tweets themselves. One possible reason (among
many) may be that the finding was spurious. The positive external 
events from Syria may have been self-serving, aiming to prevent intervention
by other countries or to cover up what was happening internally.
During these moments, the increased cohesion may reflect a surge from 
the Syrian people trying to raise awareness of the situation or
to decry the Syrian government's attempts to improve their international
standing. In this case, the increased coupling of positive events would
be coupled not with shared positive affect in social media but instead
to shared negative affect in social media in response. However, we
cannot test this hypothesis with the current data; future 
research should explore the semantic content of this tweet
corpus to determine the nature of the socially cohered language.

### 2020-06-01 manuscript.tex
Edits to crqa results

In the present study, we investigated the dynamics of real-world events
and online communication on Twitter in Syria during Arab Spring. We examined
how social mobilization both virtually and physically evolve over time in
tandem. Using the
nonlinear dynamical time series analyses, we investigated the theory that
virtual mobilization is increasingly reflective of real-world events
during times of strife.

@@

The significant result of DET for social cohesion with all and negative
events supports our hypothesis that
event salience is coupled with online social cohesion The frequency
of all and negative events are thus associated with greater
shared trajectories with social cohesion that would be expected by chance.
However, when we specifically target positive events, the connection
to social cohesion fades, providing further
support for our hypothesis. Positive events
may be less coupled to social cohesion than more salient negative events
during times of turmoil; by contrast, overall event frequency and
negative event frequency are coupled with Twitter social cohesion.

@@

While interesting, the underlying meaning or drivers of this change
in results requires further investigation that incorporates the
actual content of the tweets themselves. One possible reason (among
many) may be that the finding was spurious. The positive external
events from Syria may have been self-serving, aiming to prevent intervention
by other countries or to cover up what was happening internally.
During these moments, the increased cohesion may reflect a surge from
the Syrian people trying to raise awareness of the situation or
to decry the Syrian government's attempts to improve their international
standing. In this case, the increased coupling of positive events would
coupled not with shared positive affect in social media but instead
to shared negative affect in social media in response. However, we
cannot test this hypothesis with the current data; future\\
research should explore the semantic content of this tweet
corpus to determine the nature of the socially cohered language.

>>>>

In the present study, we investigated the dynamics of real-world events
and online communication on Twitter in Syria during Arab Spring. We examined
how social mobilization both virtually and physically evolve over time in
tandem. Using nonlinear dynamical time series analyses, we investigated the
theory that virtual mobilization is increasingly reflective of real-world
events during times of strife.

@@

The significant result of DET for social cohesion with all and negative
events supports our hypothesis that event salience is coupled with online
social cohesion. The frequency of all and negative events are thus associated
with greater shared trajectories with social cohesion that would be expected
by chance. However, when we specifically target positive events, the connection
to social cohesion fades, providing further support for our hypothesis.
Positive events may be less coupled to social cohesion than more salient
negative events during times of turmoil; by contrast, overall event frequency
and negative event frequency are coupled with Twitter social cohesion.

@@

While interesting, the underlying meaning or drivers of this change
in results requires further investigation that incorporates the
actual content of the tweets themselves. One possible reason (among
many) may be that the finding was spurious. The positive external
events from Syria may have been self-serving, aiming to prevent intervention
by other countries or to cover up what was happening internally.
During these moments, the increased cohesion may reflect a surge from
the Syrian people trying to raise awareness of the situation or
to decry the Syrian government's attempts to improve their international
standing. In this case, the increased coupling of positive events would
be coupled not with shared positive affect in social media but instead
to shared negative affect in social media in response. However, we
cannot test this hypothesis with the current data; future
research should explore the semantic content of this tweet
corpus to determine the nature of the socially cohered language.
